---
title: "realtR"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation
```{r, eval=F}
devtools::install_github("abresler/requestsR")
devtools::install_github("abresler/realtR")
```

## Requirements

This package handles some complicated web request tasks and because of this
in order to use this package you need a working version of Python, the requests module and my [requestsR](https://github.com/abresler/requestsR) 
package.

### realtR

There are few service industries worse than the residential real estate brokerage industry.  

Industy actors generally are some of the most overpaid, dishonest, people you will come across.  They generally hoard information, make-up information, aren't held accountable and often time have no idea what is actually going in the market.  They are a cartel and ensure regardless of what happens, if a transaction closes they get paid.  

The consumer has a hard time educating themselves and can be at the mercy of these snake-oil salesmen.

The time has come to change that and `realtR` goes a **long** way towards doing that by empowering anyone who knows a bit of R with API wrappers giving you access to nearly all of the available information on listings throughout the United States and much much more.

In a few lines of code you will have as much or more information than brokers and you can use it however you chose but my intention is to help you hold your broker accountable.

In addition to listing data the package provides users access to the most robust geocoding tool I have ever come across and a host of market information.


## Functions

* `geocode()` - 
* `listing_counts()` -
* `listings()` - 
* `vitality()` - 
* `trends()` - 
* `map_listings()` - 
* `median_prices()` -
* `market_trends()` - 